---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


## Overview

`"binomial"` is a minimal [R](http://www.r-project.org/) package 
that provides functions to simulate binomial distribution.

* `bin_variable()` creates a binomial object (of class `"binvar"`)
* `bin_mean()` calculate the mean of a binomial distribution
* `bin_variance()` calculate the variance of a binomial distribution
* `bin_skewness()` calculate the skeeness of a binomial distribution
* `bin_mode()` calculate the mdoe of a binomial distribution
* `bin_kurtosis()` calculate the kurtosis of a binomial distribution
* `bin_distribution()` creates a binomial distribution object (of class `"bindis"`)
* `bin_cumulative()` creates a binomial cumulative probability object (of class `"bincum"`)
* `plot()` method for `"bindis"` and `"bindis"` objects to plot probability graphs
* `summary` method for a `"binvar"` object to create a summary.



## Motivation

This package has been developed to illustrate statistic information 


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("binomial") 
# install "binomial" (without vignettes)
devtools::install_github("stat133-sp19/hw-stat133-garyhu9718/tree/master/workout3/binomial")
# install "binomial" (with vignettes)
devtools::install_github("stat133-sp19/hw-stat133-garyhu9718/tree/master/workout3/binomial", build_vignettes = TRUE)
```


## Usage

```{r}
library(binomial)
#create binomial obeject
s1 = bin_variable(5,0.5)
s1

#summarize the object
summary(s1)

#calculate the basic statistic information
bin_mean(5,0.5)
bin_variance(5,0.5)
bin_mode(5,0.5)
bin_skewness(5,0.5)
bin_kurtosis(5,0.5)

#create a bindis object and plot it 
s2 = bin_distribution(5,0.5)
s2
p1 = plot(s2)

#create a bincum object and plot it 
s3 = bin_cumulative(5,0.5)
s3
p2 = plot(s3)
```