---
title: "introduction"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(binomial)
```

##Binomial 

The package `"binomial"`is a package sketching random variables that follow the binomial distribution.The package includes a series of functions summarizing the statistic information and creating simulation.

##Calculating the choosing number

In binomial distribution, there is a necessaty to calculate the number of combinations of k objects from a population of n objects. For that sake, we have function bin_choose(), here is an example when n = 10, k = 3:
```{r}
bin_choose(n = 10,k = 3)
```

Also, we can vetorize the process like:
```{r}
bin_choose(10,1:3)
```
That will create a vector consisting of the choosing number of 1,2 and 3 objects.

##The probability 
One of the questions we care on the binomial distributon is the probability of outcome with a certain number of success, there is a function bin_probability that achieves this in the way below:
```{r}
bin_probability(n = 10, k=4, p = 0.1)
```

Similarly, we can vertorize the process:
```{r}
bin_probability(10,1:3,0.1)
```

##Binomial variable
Given the probability of single success and the total number of trials, we use the function bin_variable() to form a binvar object representing a binomial distribution, which is a list consisting of the trial times and probability.
```{r}
bin_variable(10,0.1)
```

###Printing method for the binvar object 
To better illustrate information of the binvar object, we redefine the printing method for it.
```{r}
print(bin_variable(10,0.1))
```
###Summary of the binvar
A customized method to summarize the distribution is created in the package, by inputting the binvar object, we can get a list containing the basic statistic information of the distribution. Besides, we give this kind of list a certain class called summary.binvar, and designed printing method for it.
```{r}
s = summary(bin_variable(10,0.5))
s
```

##Binomial ditribution
bin_distribution is a function that using the give trial times and probability of single trial's success to form a data fram recording the times of success and corresponding probability.
```{r}
s2 = bin_distribution(5,0.5)
s2
```

And a defined plot method can be used to get the bar chart.
```{r}
plot(s2)
```

##Binomial cumulative 
Function bin_cumulative is designed to illustrate the cumulative probability of the ditribution. A plotting method is also provided.
```{r}
s3 = bin_cumulative(10,0.1)
s3
plot(s3)
```
